Nature or Nurture? Collisionless Evolution of Galactic Disc-Halo Systems

### 2019-09-14 Thesis/Conclusion.tex
Most corrections implemented; expanding discussions tomorrow

\section{Disk-Halo Interactions}

@@

One of the key contributions of this thesis is the understanding of how the dynamic nature of stellar disks affects halo properties, as studied in Chapter~\ref{ch:paper_i}. Some halo properties, such as the distribution of mass in the inner halo, depend a lot on how the disk is modelled. This is very evident in the differences in adiabatic contraction between the rigid and live disks. Specifically, we find the formation of a bar led to a more concentrated halo mass distribution. On the whole, these results suggest that if one is interested in the Core-Cusp problem, this should be studied with fully live models of stellar disks.

The intermediate-to-outer halo is less effected by the dynamics of the inner halo. While some differences between our disk potential models were observed in the halo mass functions, these differences were minor. The details of how satellites are disrupted appear to be at least weakly dependent on how the disk is modelled, and stream studies should consider as realistic of a disk as possible. This last aspect of our work has informed some design decisions by others, namely in the work of \citet{read_2019}. If one is just interested in subhalo population statistics, it is sufficient to model baryons as fixed potentials in a pure dark matter halo.

The global picture painted by our work is that modelling the disk as a rigid body does well in determining how the disk settles (i.e. its angular motion), a result consistent with \citet{DubinskiKuijkenRigidDisks}. It appears that the formation of a bar in the live disk is the most substantial difference between the rigid and live disks' effects on the inner halo, a difference that only becomes significant \textit{after} the the live disk

@@

Our algorithm makes optimizations over previous disk insertion schemes. The optimizations we made are by no means exhaustive, and a detailed discussion of potential optimizations is given in Chapter~\ref{ch:implementation}. We focus here on scientific concerns with our algorithm, rather than performance optimizations.

The scheme as specified has the undesirable property of adding angular momentum and mass to the halo. This happens when the disk grows, and we fail to extract mass and angular momentum from the halo\footnote{Note that dark matter particles dark matter only simulations include the baryon mass of the Universe.}. A potential improvement which extracts mass and angular momentum from the halo particles during the disk growth phase would alleviate these concerns. This may have a sizable impact on our conclusions about the disk's effect on adiabatic contraction, since both the disk and halo are dominant in the inner galaxy.

We might also consider a scheme which initializes the disk with some gas component. \citet{deg_2019} modified \textsc{GalactICS} to allow for the inclusion of gas. This, combined with modifying halo particle masses, should allow us to more accurately compare our results to fully hydrodynamical \textit{ab initio} simulations.

A valid criticism of our disk insertion technique is that all of the stars are initialized simultaneously. This is unrealistic, and allowing stars to gradually form out of the rigid disk potential might show a more complicated dependence on the initial conditions parameter space. In fact, \citet{aumer_2016} grow disks in a similar fashion and find that slowly growing the disk along with gas physics impacts important properties like bar formation. In some cases it may even shut off bar formation, which we believe would substantially impact our conclusions about adiabatic contraction.

Even with the current algorithm, there is more we can do on the study of disk-halo interactions. A possible project would be to study the effect of varying disk properties in the same halo. We might also consider adding a spheroidal bulge component to see how high baryonic mass concentrations change our results. We might also look for more detailed evidence of the halo's response to the disk in our existing simulations in the form of wakes. This kind of response was explored in one of our toy models in Chapter~\ref{ch:paper_iii}, and it seems natural to extend this analysis to our cosmological simulations.

@@

We discuss our contributions to understanding how bars form in stellar disks in Chapter~\ref{ch:paper_ii}. The paper unifies previous work on disk insertion schemes by viewing them through a lens of a common parameter space. Through placing our models and the models of \citet{YurinSpringelStellarDisks} in this space, we are able to contextualize the very large bars formed in their study. In particular, we show that a commonly discounted variable, the disk thickness, is a primary driver of bar strength in a cosmological setting. We show that, in general, the length of a bar at present day for cosmological stellar disks is largely a function of the initial disk thickness. This effect is not numerical, as we show through our application of the \textsc{AGAMA} code \citep{vasiliev_2018}.

The importance of being cautious about the choice of gravitational softening length is also illustrated. Since disk thickness appears to play a major role in bar formation in $\Lambda$CDM, we must be careful that we are resolving our disks' vertical structure.

On the whole, we show that it is difficult to suppress the formation of bars in a cosmological setting. While the bar more closely resemble the Milky Way's when we start with a thinner disk, we find strong bars form nonetheless. As such, there is still a discrepancy in accounting for the observed bar fraction without invoking classical bulges or non-collisionless phenomena. Our work has proved useful in illustrating this, and we are credited for furthering discussion of this issue in \citet{sellwood_2019}.

We manage to bolster this result in Chapter~\ref{ch:paper_iii}, where we ran twelve simulations in four halos. Although all of the halos had the same total mass as the Milky Way, they varied widely in terms of their other properties. Despite the differences in the halos, the bars formed by embedded disks were quite similar. Additionally, there is a nontrivial dependence on Toomre $Q$ in terms of when the bar buckles, but the final bar strength depends very weakly on this parameter, contrary to \citet{YurinSpringelStellarDisks}. Rather, the trend \citet{YurinSpringelStellarDisks} sees in $Q$ is likely due to the presence of their bulge simulations, which would increase $Q$ as well as provide a stabilizing central mass.

@@

In Chapter~\ref{ch:paper_iii}, bar formation is not the focus of the study. Now that we have a sample of bars forming in different cosmological environments, we can position the disks in the parameter space described in Chapter~\ref{ch:paper_ii}. A proper synthesis with previous literature on this topic should be performed.

@@

It would also be interesting to see how implementing a hydrodynamical, growing disk described in \S\ref{ssec:conclusions_insertion} would change our results. An interesting conclusion from \citet{aumer_2016} was that bar formation could be suppressed by GMCs. It is worth noting that these simulations also included a compact bulge, and the result might be different for a pure disk-halo system in a fully cosmological environment. The author's view is that moving in this direction is the next logical step for disk-insertion schemes.

@@

The main focus of Chapter~\ref{ch:paper_iii} is how disks form vertical structure in $\Lambda$CDM environments. We showed that there are a wide variety of Milky Way-mass halos that form vertical structure consistent with structure observed in the solar neighborhood. In particular, we showed that this structure can be formed without a massive satellite encounter in a cosmological setting. This position is bolstered by the fact that we see Monoceros-like structure in all twelve of our simulations.

We also find that consistent perpendicular torques on the disk are required to explain features in the outer disk. It is unlikely that substructures far below the $10^{11}$ solar mass regime are responsible for stars stripped to higher latitudes. Global tides from disk-halo axis misalignment seem to be the most effective way to create these populations of stars. We therefore suggest that streams originating from the outer disk may primarily depend on the Milky Way's interaction with the LMC. A massive merger like the one with the LMC can cause consistent perpendicular torques its own tides or by disturbing the existing smooth Milky Way halo mass.

@@

A key flaw in this work is that we had no LMC analogues. An interesting experiment would be to compare the vertical structure caused by a future LMC merger and the vertical structure generated when a disk is misaligned in a triaxial halo. On the whole, future work should proceed in the same way as the work in Chapter~\ref{ch:paper_ii}. We should seek to relate the halo environments to a common parameter space.

@@

This work presents an improved disk insertion scheme with applications to Galactic astronomy. We have successfully shown that we can set up and understand disks inserted into cosmological halos. Future work is suggested, and we have no shortage of potential projects to improve our scheme. The long-term goal of this work is to bridge the gap with \textit{ab initio} simulations, and we have presented a clear roadmap for doing so.

As simulation resolutions and computing power improve, we may be forced to revisit the fundamentals at the beginning of Chapter~\ref{ch:background}. Simulation codes may need to be redesigned to accommodate ever-increasing needs to relate them to observations. Our hope is that disk insertion schemes will be at the heart of these discussions as a valuable tool in understanding observational data.

>>>>

\section{Disc-Halo Interactions}

@@

One of the key contributions of this thesis is the understanding of how the dynamic nature of stellar discs affects halo properties, as studied in Chapter~\ref{ch:paper_i}. Some halo properties, such as the distribution of mass in the inner halo, depend a lot on how the disc is modelled. This is very evident in the differences in adiabatic contraction between the rigid and live discs. Specifically, we find the formation of a bar led to a more concentrated halo mass distribution. On the whole, these results suggest that if one is interested in the Core-Cusp problem, this should be studied with fully live models of stellar discs.

The intermediate-to-outer halo is less effected by the dynamics of the inner halo. While some differences between our disc potential models were observed in the halo mass functions, these differences were minor. The details of how satellites are disrupted appear to be at least weakly dependent on how the disc is modelled, and stream studies should consider as realistic of a disc as possible. This last aspect of our work has informed some design decisions by others, namely in the work of \citet{read_2019}. If one is just interested in subhalo population statistics, it is sufficient to model baryons as fixed potentials in a pure dark matter halo.

The global picture painted by our work is that modelling the disc as a rigid body does well in determining how the disc settles (i.e. its angular motion), a result consistent with \citet{DubinskiKuijkenRigidDisks}. It appears that the formation of a bar in the live disc is the most substantial difference between the rigid and live discs' effects on the inner halo, a difference that only becomes significant \textit{after} the the live disc

@@

Our algorithm makes optimizations over previous disc insertion schemes. The optimizations we made are by no means exhaustive, and a detailed discussion of potential optimizations is given in Chapter~\ref{ch:implementation}. We focus here on scientific concerns with our algorithm, rather than performance optimizations.

The scheme as specified has the undesirable property of adding angular momentum and mass to the halo. This happens when the disc grows, and we fail to extract mass and angular momentum from the halo\footnote{Note that dark matter particles dark matter only simulations include the baryon mass of the Universe.}. A potential improvement which extracts mass and angular momentum from the halo particles during the disc growth phase would alleviate these concerns. This may have a sizable impact on our conclusions about the disc's effect on adiabatic contraction, since both the disc and halo are dominant in the inner galaxy.

We might also consider a scheme which initializes the disc with some gas component. \citet{deg_2019} modified \textsc{GalactICS} to allow for the inclusion of gas. This, combined with modifying halo particle masses, should allow us to more accurately compare our results to fully hydrodynamical \textit{ab initio} simulations.

A valid criticism of our disc insertion technique is that all of the stars are initialized simultaneously. This is unrealistic, and allowing stars to gradually form out of the rigid disc potential might show a more complicated dependence on the initial conditions parameter space. In fact, \citet{aumer_2016} grow discs in a similar fashion and find that slowly growing the disc along with gas physics impacts important properties like bar formation. In some cases it may even shut off bar formation, which we believe would substantially impact our conclusions about adiabatic contraction.

Even with the current algorithm, there is more we can do on the study of disc-halo interactions. A possible project would be to study the effect of varying disc properties in the same halo. We might also consider adding a spheroidal bulge component to see how high baryonic mass concentrations change our results. We might also look for more detailed evidence of the halo's response to the disc in our existing simulations in the form of wakes. This kind of response was explored in one of our toy models in Chapter~\ref{ch:paper_iii}, and it seems natural to extend this analysis to our cosmological simulations.

@@

We discuss our contributions to understanding how bars form in stellar discs in Chapter~\ref{ch:paper_ii}. The paper unifies previous work on disc insertion schemes by viewing them through a lens of a common parameter space. Through placing our models and the models of \citet{YurinSpringelStellarDisks} in this space, we are able to contextualize the very large bars formed in their study. In particular, we show that a commonly discounted variable, the disc thickness, is a primary driver of bar strength in a cosmological setting. We show that, in general, the length of a bar at present day for cosmological stellar discs is largely a function of the initial disc thickness. This effect is not numerical, as we show through our application of the \textsc{AGAMA} code \citep{vasiliev_2018}.

The importance of being cautious about the choice of gravitational softening length is also illustrated. Since disc thickness appears to play a major role in bar formation in $\Lambda$CDM, we must be careful that we are resolving our discs' vertical structure.

On the whole, we show that it is difficult to suppress the formation of bars in a cosmological setting. While the bar more closely resemble the Milky Way's when we start with a thinner disc, we find strong bars form nonetheless. As such, there is still a discrepancy in accounting for the observed bar fraction without invoking classical bulges or non-collisionless phenomena. Our work has proved useful in illustrating this, and we are credited for furthering discussion of this issue in \citet{sellwood_2019}.

We manage to bolster this result in Chapter~\ref{ch:paper_iii}, where we ran twelve simulations in four halos. Although all of the halos had the same total mass as the Milky Way, they varied widely in terms of their other properties. Despite the differences in the halos, the bars formed by embedded discs were quite similar. Additionally, there is a nontrivial dependence on Toomre $Q$ in terms of when the bar buckles, but the final bar strength depends very weakly on this parameter, contrary to \citet{YurinSpringelStellarDisks}. Rather, the trend \citet{YurinSpringelStellarDisks} sees in $Q$ is likely due to the presence of their bulge simulations, which would increase $Q$ as well as provide a stabilizing central mass.

@@

In Chapter~\ref{ch:paper_iii}, bar formation is not the focus of the study. Now that we have a sample of bars forming in different cosmological environments, we can position the discs in the parameter space described in Chapter~\ref{ch:paper_ii}. A proper synthesis with previous literature on this topic should be performed.

@@

It would also be interesting to see how implementing a hydrodynamical, growing disc described in \S\ref{ssec:conclusions_insertion} would change our results. An interesting conclusion from \citet{aumer_2016} was that bar formation could be suppressed by GMCs. It is worth noting that these simulations also included a compact bulge, and the result might be different for a pure disc-halo system in a fully cosmological environment. The author's view is that moving in this direction is the next logical step for disc-insertion schemes.

@@

The main focus of Chapter~\ref{ch:paper_iii} is how discs form vertical structure in $\Lambda$CDM environments. We showed that there are a wide variety of Milky Way-mass halos that form vertical structure consistent with structure observed in the solar neighborhood. In particular, we showed that this structure can be formed without a massive satellite encounter in a cosmological setting. This position is bolstered by the fact that we see Monoceros-like structure in all twelve of our simulations.

We also find that consistent perpendicular torques on the disc are required to explain features in the outer disc. It is unlikely that substructures far below the $10^{11}$ solar mass regime are responsible for stars stripped to higher latitudes. Global tides from disc-halo axis misalignment seem to be the most effective way to create these populations of stars. We therefore suggest that streams originating from the outer disc may primarily depend on the Milky Way's interaction with the LMC. A massive merger like the one with the LMC can cause consistent perpendicular torques its own tides or by disturbing the existing smooth Milky Way halo mass.

@@

A key flaw in this work is that we had no LMC analogues. An interesting experiment would be to compare the vertical structure caused by a future LMC merger and the vertical structure generated when a disc is misaligned in a triaxial halo. On the whole, future work should proceed in the same way as the work in Chapter~\ref{ch:paper_ii}. We should seek to relate the halo environments to a common parameter space.

@@

This work presents an improved disc insertion scheme with applications to Galactic astronomy. We have successfully shown that we can set up and understand discs inserted into cosmological halos. Future work is suggested, and we have no shortage of potential projects to improve our scheme. The long-term goal of this work is to bridge the gap with \textit{ab initio} simulations, and we have presented a clear roadmap for doing so.

As simulation resolutions and computing power improve, we may be forced to revisit the fundamentals at the beginning of Chapter~\ref{ch:background}. Simulation codes may need to be redesigned to accommodate ever-increasing needs to relate them to observations. Our hope is that disc insertion schemes will be at the heart of these discussions as a valuable tool in understanding observational data.

### 2019-09-14 Thesis/Introduction.tex
Most corrections implemented; expanding discussions tomorrow

Although dark matter makes up 84\% of the matter, matter only makes up 31.5\% of the present day Universe's total energy density. The remainder contains a modest contribution from radiation, but the bulk is comprised of unaccounted dark energy \citep{kolb_turner,dodelson, BT}. Dark energy, whatever it is, is responsible for the accelerating expansion of the Universe, something we first learned from from observations of Type 1a supernova \citep{reiss_1998,perlmutter_1999}. Modern cosmology is a struggle between the competing forces of dark matter and dark energy, and both have implications for the local dynamics in the Universe.

@@

The baryons, interacting through baryon acoustic oscillations (BOA), are delayed in falling into the potential wells made by the dark matter. As the baryons fall into the centers of the potential wells over time, the cores of the dark matter distributions, comprised of spheroidal structures called halos, contract. After infall into a dark matter halo, the baryons cool to the point where stars are able to form. This is how the first galaxies formed.

@@

We broadly commented on the hierarchical formation of galaxies. Over time, galaxies that merge with other galaxies should become well-mixed in the host halo. That is, there should be an underlying smooth distribution of mass in which all of the subhalos reside. A key prediction of $\Lambda$CDM is that this smooth distribution should have a universal density profile in the limit that dark matter dominates the Universe \citep{nfw}. Furthermore, the dark matter should have a density distribution somewhat resembling a squashed football, a spheroid flattened on two axes. Whether or not this picture holds observationally in real galaxies is an open problem. The density profile proposed by \citet{nfw} is cuspy at the center, whereas some observations are more consistent with a flatter central density \citep{de_blok_core_cusp}. Astronomers have dubbed this the Core-Cusp Problem.

@@

Since dark matter is not directly probable, we must use indirect methods to infer information about the halo. In addition to the dark matter halo, our Galaxy is composed of baryons in the form of a central spheroidal bulge, a thin gas disk, a thin stellar disk, and a more diffuse thick stellar disk. There is also a stellar component of the halo, which contains remnants of old mergers and star clusters known as globular clusters. This section is organized by talking about tidal disruption of subhalos in the Galactic halo, the dynamics of the central part of the Galaxy, and vertical structure in the Galactic disk. How the cosmological environment effects these observables is the bulk of this thesis, and we motivate here why these aspects are the subject of focus.

@@

More streams have been discovered since then, and a few notable ones are the Orphan Stream \citep{grillmair_2006,belokurov_2007,newberg_2010}, remarkable for its apparent lack of progenitor, TriAnd, A13, and the Monoceros Ring. This is by no means a complete accounting of known stellar streams. Something on the order of nearly a hundred known to exist in the Milky Way alone \citep{sanders_binney_2013_a, ibata_2019}. While streams alone have been useful in getting some broad constraints on the Galactic potential and geometry of the halo, complications arise from the fact that streams do not follow orbits exactly \citet{sanders_binney_2013_a} and the fact that the Milky Way potential is predicted from theory to be time dependent.

@@

%With the Sagittarius stream specifically, there 
\subsection{Response of the Galactic Disk to the Cosmological Environment}

We might also attempt to infer properties of the subhalo population through their effect on the Galactic disc.  It is believed that the affect of the Milky Way's substructure population can be observed as waves-like behaviour in the thin disc's vertical structure \citep{widrow_2012_sdss,carlin_2013_lamost, williams_2013_rave,xu_2015, carrillo_2018_rave}.  These waves can manifest as small corrugations in the Galactic disc, as global bending and breathing motions, or even as large warps in the Milky Way's gas  \citep{gasWarp} and stellar discs. It is worth noting that these observations are being confirmed in DR2 of the Gaia mission \citep[for example]{gaia_collab,bennet_2019_gaia}.

@@

\section{Disk Insertion Techniques for Cosmology}

@@

The thesis is organized in the following manner. In Chapter~\ref{ch:background}, we reduce the necessary theoretical background to understand this work to a succinct summary. Following this, in Chapter~\ref{ch:paper_i}, we explore the first peer-reviewed paper on which this thesis is based. It outlines the disk insertion scheme and comments on how the dynamic nature of the Milky Way's stellar disk should affect its inner halo. Chapter~\ref{ch:paper_ii} presents the second published paper which focuses on the question of how stable disks are against forming bars in a cosmological setting. A final paper is presented in Chapter~\ref{ch:paper_iii}, where we look at how disks form vertical structure in a cosmological setting. We conclude with summaries and ideas for future work in Chapter~\ref{ch:conclusion}.

>>>>

Although dark matter makes up 84\% of the matter, matter only makes up 31.5\% of the present day Universe's total energy density. The remainder contains a modest contribution from radiation, but the bulk is comprised of unaccounted dark energy \citep{kolb_turner,dodelson, BT}. Dark energy, whatever it is, is responsible for the accelerating expansion of the Universe, something we first learned from observations of Type 1a supernova \citep{reiss_1998,perlmutter_1999}. Modern cosmology is a struggle between the competing forces of dark matter and dark energy, and both have implications for the local dynamics in the Universe.

@@

The baryons, interacting through baryon acoustic oscillations (BAO), are delayed in falling into the potential wells made by the dark matter. As the baryons fall into the centers of the potential wells over time, the cores of the dark matter distributions, comprised of spheroidal structures called halos, contract. After infall into a dark matter halo, the baryons cool to the point where stars are able to form. This is how the first galaxies formed.

@@

We broadly commented on the hierarchical formation of galaxies. Over time, galaxies that merge with other galaxies should become well-mixed in the host halo. That is, there should be an underlying smooth distribution of mass in which all of the subhalos reside. A key prediction of $\Lambda$CDM is that this smooth distribution should have a universal density profile in the limit that dark matter dominates the Universe \citep{nfw}. Furthermore, the dark matter should have a density distribution somewhat resembling a squashed football, a spheroid flattened on two axes, in general. There are, in fact, the special cases of being either perfectly spherical, prolate, or oblate. Whether or not this picture holds observationally in real galaxies is an open problem. The density profile proposed by \citet{nfw} is cuspy at the center, whereas some observations are more consistent with a flatter central density \citep{de_blok_core_cusp}. Astronomers have dubbed this the Core-Cusp Problem.

@@

Since dark matter is not directly probable, we must use indirect methods to infer information about the halo. For this, we need to know something about the distribution of mass in the Galaxy.

\subsection{Distribution of Mass in the Milky Way}

In addition to the dark matter halo, our Galaxy is composed of baryons in the form of a central spheroidal bulge, a thin gas disc, a thin stellar disc, and a more diffuse thick stellar disc. The thin stellar disc is where the majority of our work is focused. We see a wide variety of structure in the stellar discs of other galaxies, as well as our own Milky Way. For example, the center of our galaxy is believed to contain a stellar bar, a bar-like component of the thin disc \citep{BT}. There are also non-planar features in stellar discs, such as warps \citep{BT}. How these features come into being is a main focus of this thesis.\footnote{For an in-depth discussion of the features arising in stellar discs, \citet{Sellwood2013} presents a fantastic review.}

There is also a stellar component of the halo, which contains remnants of old mergers and star clusters known as globular clusters. This section is organized by talking about tidal disruption of subhalos in the Galactic halo, the dynamics of the central part of the Galaxy, and vertical structure in the Galactic disc. How the cosmological environment effects these observables is the bulk of this thesis, and we motivate here why these aspects are the subject of focus.

@@

More streams have been discovered since then, and a few notable ones are the Orphan Stream \citep{grillmair_2006,belokurov_2007,newberg_2010}, remarkable for its apparent lack of progenitor, TriAnd, A13, and the Monoceros Ring. This is by no means a complete accounting of known stellar streams. Something on the order of nearly a hundred known to exist in the Milky Way alone \citep{sanders_binney_2013_a, ibata_2019}. While streams alone have been useful in getting some broad constraints on the Galactic potential and geometry of the halo, complications arise from the fact that streams do not follow orbits exactly \citep{sanders_binney_2013_a} and the fact that the Milky Way potential is predicted from theory to be time dependent.

@@

%With the Sagittarius stream specifically, there 
\subsection{Response of the Galactic Disc to the Cosmological Environment}

We might also attempt to infer properties of the subhalo population through their effect on the Galactic disc.  It is believed that the affect of the Milky Way's substructure population can be observed as wave-like behaviour in the thin disc's vertical structure \citep{widrow_2012_sdss,carlin_2013_lamost, williams_2013_rave,xu_2015, carrillo_2018_rave}.  These waves can manifest as small corrugations in the Galactic disc, as global bending and breathing motions, or even as large warps in the Milky Way's gas  \citep{gasWarp} and stellar discs. It is worth noting that these observations are being confirmed in DR2 of the Gaia mission \citep[for example]{gaia_collab,bennet_2019_gaia}.

@@

\section{Disc Insertion Techniques for Cosmology}

@@

The thesis is organized in the following manner. In Chapter~\ref{ch:background}, we reduce the necessary theoretical background to understand this work to a succinct summary. Following this, in Chapter~\ref{ch:paper_i}, we explore the first peer-reviewed paper on which this thesis is based. It outlines the disc insertion scheme and comments on how the dynamic nature of the Milky Way's stellar disc should affect its inner halo. Chapter~\ref{ch:paper_ii} presents the second published paper which focuses on the question of how stable disks are against forming bars in a cosmological setting. A final paper is presented in Chapter~\ref{ch:paper_iii}, where we look at how disks form vertical structure in a cosmological setting. We conclude with summaries and ideas for future work in Chapter~\ref{ch:conclusion}.

### 2019-09-14 Thesis/Paper_I.tex
Most corrections implemented; expanding discussions tomorrow

\begin{figure}
\centering 
\includegraphics[width=1.\textwidth]{../figures/all_rotation_curves_five_sims}
\caption{Circular speed curve decompositions at $z=1$ (top row) and
  $z=0$ (bottom row) for (from left to right) our LD, RD, and MN
  simulations.  Halo contributions are represented as dot-dashed
  lines, disc contributions are represented by dashed lines, and the
  total rotation curve is given by a solid line.  For reference, we have
  included the circular speed curve for the DMO halo (dot-dashed curve).}
\label{fig:rotation_curves}
\end{figure}

@@

Evidently, the MN halo is rounder, especially in the inner part, the
the FO halo.  Recall that the main difference between these two cases
is that the MN disc is pinned to the potential minimum of the halo.
It is perhaps not surprising then that, as with adiabatic contraction,
it has a stronger effect on the halo's shape.  
We also note that the axis ratio profiles for the RD and LD simulations
are fairly similar.

>>>>

\begin{figure}
\centering 
\includegraphics[width=1.\textwidth]{../figures/all_rotation_curves_five_sims}
\caption{Circular speed curve decompositions at $z=1$ (top row) and
  $z=0$ (bottom row) for (from left to right) our MN, FO, RD, and LD
  simulations.  Halo contributions are represented as dot-dashed
  lines, disc contributions are represented by dashed lines, and the
  total rotation curve is given by a solid line.  For reference, we have
  included the circular speed curve for the DMO halo (dot-dashed curve).}
\label{fig:rotation_curves}
\end{figure}

@@

Evidently, the MN halo is rounder, especially in the inner part, than
the FO halo.  Recall that the main difference between these two cases
is that the MN disc is pinned to the potential minimum of the halo.
It is perhaps not surprising then that, as with adiabatic contraction,
it has a stronger effect on the halo's shape.  
We also note that the axis ratio profiles for the RD and LD simulations
are fairly similar.

### 2019-09-14 Thesis/Paper_II.tex
Most corrections implemented; expanding discussions tomorrow

Fig. \ref{fig:isolated_a2_vs_t} encapsulates bar strength into a
single number, the mean $m=2$ Fourier amplitude inside $2.2$ disc
scale lengths, or about $5.5\,{\rm kpc}$.  A more complete picture of
bar strength is presented in Fig.\,\ref{fig:isolated_r_t_a2} where we
plot $A_2$ as a function of $R$ and $t$. The figure is constructed by
calculating $c_2$ (Eq.\,\ref{eq:cm}) for cylindrical rings of radius
$200\,{\rm pc}$.  Also shown is the corotation radius, which is
determined from the pattern speed $\Omega_p$ and rotation curve. The
former is given by a numerical estimate of ${\text{d}
  \phi_2}/{\text{d} t}$; corotation is found by determining the radius
at which $\Omega_p = V_c/R$.  Thus, since our galaxy models have
roughly flat rotation curves beyond $5\,{\rm kpc}$, the corotation
essentially gives the inverse patter speed or pattern period.

>>>>

Fig. \ref{fig:isolated_a2_vs_t} encapsulates bar strength into a
single number, the mean $m=2$ Fourier amplitude inside $2.2$ disc
scale lengths, or about $5.5\,{\rm kpc}$.  A more complete picture of
bar strength is presented in Fig.\,\ref{fig:isolated_r_t_a2} where we
plot $A_2$ as a function of $R$ and $t$. The figure is constructed by
calculating $c_2$ (Eq.\,\ref{eq:cm}) for cylindrical rings of radius
$200\,{\rm pc}$.  Also shown is the corotation radius, which is
determined from the pattern speed $\Omega_p$ and rotation curve. The
former is given by a numerical estimate of ${\text{d}
  \phi_2}/{\text{d} t}$; corotation is found by determining the radius
at which $\Omega_p = V_c/R$.  Thus, since our galaxy models have
roughly flat rotation curves beyond $5\,{\rm kpc}$, the corotation
essentially gives the inverse pattern speed or pattern period.
